An Efficient Construction of the Prefer-Max Sequence and of an Infinite de Bruijn Sequence

### 2017-01-02 paper.tex
Lyndon + bibliography

The

>>>>

This result allows for another construction of the reversed prefer-max sequence, as follows. By the definition of the necklace joining construction, shown in Algorithm~\ref{necklace-joining}, one can infer that key words appear in lexicographic order and that the distance between one key words to the next is the size of the necklace of the latter. For a word $w\in\N^n$, let the \emph{primitive root} of $w$ be the  unique primitive (non-periodic) word $\rho(w)$ such that $w = \rho(w)^l$ for some $l \geq 1$. Since the length of the primitive root of a ket word is the length of its cycle, we get the following construction:

\begin{algorithm}[!h]
	Construct an infinite sequence of symbols by concatenating the primitive roots  of the key words of length $n$ in left-to-right lexicographic order.
	\caption{Word concatenation construction.}
	\label{word-concatenation}
\end{algorithm}

As the reader may expect, our result is this sequence is also the reverse of the prefer-max sequence:

\begin{theorem}
	The sequence described in Algoithm~\ref{word-concatenation} is the same sequence described in Algorithm~\ref{inf-construction}.
\end{theorem}

The last result is similar in nature to the theorem of Fredricksen and Maiorana in~\cite{Fredricksen1978} (see also~\cite{Moreno2004} and~\cite{Moreno2015}).	
These paper contain proofs that the concatenation of Lyndon words (words that are minimal in lexicographic among their rotations) of length dividing $n$ in lexicographic order produces a de Bruijn sequence of span $n$, and they state that this word is lexicographically minimal among all
de Bruijn sequences of span $n$.

\bibliography{library}{}
\bibliographystyle{plain}
